%!TEX TS-program = xelatex

\documentclass{cv}
\usepackage{etoolbox}

\usepackage{pst-barcode}
\usepackage{hyperref}
\usepackage{auto-pst-pdf}
\usepackage[left=6.1cm,top=2cm,right=1.5cm,bottom=1.5cm,nohead,nofoot]{geometry}


%\usepackage{xcolor}
%\usepackage[usenames,dvipsnames]{xcolor}
\begin{document}
\header{nikta}{javanfar}
	{nikta.javanfar@gmail.com 613.888.8654}
      
% In the aside, each new line forces a line break
\begin{aside}
 \section{online}
 \href{http://niktajavanfar.com}{niktajavanfar.com}
 \href{http://twitter.com/niktajavanfar}{@niktajavanfar}
~
~
~
~
~
  \section{computers}
	Comfortable with OS X, Linux, Windows
~	
~
~
~
~
  \section{thesis}
	\emph{Static Fluid Spheres and the Cosmological Constant}---involved independent research in the field of general relativity
~
~
~
~
~
  \section{product demo}
 An example of a real-time dashboard \\ can be found at \href{http://lbr.boldstreet.com/Dashboards/viewer.htm?dash=r53o8}{http://lbr.boldstreet.com \\ /Dashboards/viewer.htm\\?dash=r53o8}
~	
~
~
~
~
   \section{other}
    	Violinist, \\Commuting cyclist
\end{aside}

As a product manager, my aim is to bring clarity to any project I work on, and to align all team members on the product vision.

\section{highlights of qualifications}
\begin{trivlist}
\item Building and maintaining relationships with high-profile customers and partners, including: Starbucks, Telus, and Bell.
\item Entrusted with the management of a B2B, foot-traffic analytics product consisting of real-time dashboards and historical reports, aimed at increasing consumer engagement.
\item Retained as one of eight employees upon the acquisition of BOLDstreet Wireless.
\item Strong statistical and analytical background rooted in a Bachelor's degree in Mathematical Physics. 
\item Demonstrates data-driven decision making throughout product lifecycles: from market research to customer feedback. 
\item Experience with Google Analytics, LaTeX, SQL Server Management Studio, Asana, AtTask, and D3.
\end{trivlist}
\section{education}
\begin{entrylist}
  \entry{2008-2012}{B.Sc. Honours, Queen's University}{}{Mathematical Physics}
\end{entrylist}

\section{work experience}
\begin{entrylist}
  \entry
    {2014-Present}
    {\emph{Product Manager}}
    {Datavalet Technologies}
    {Responsible for the management and oversight of a growing portfolio of commercial Wi-Fi and analytics products.}\\
      \entry
    {2013-2014}
    {\emph{Product Manager}}
    {BOLDstreet Wireless}
    {Worked closely with customers and partners in order to ensure that a foot-traffic analytics product was staying relevant in a rapidly changing industry.}\\
  \entry
    {Summer 2011} 
   {\emph{Student Researcher}}
    {Royal Military College of Canada}
    {Presented preliminary research on magnetic field detection in stars at the Women in Physics conference held at Perimeter Institute for Theoretical Physics, Waterloo, ON. }\\
  \entry
    {Summer 2010}
    {\emph{Student Researcher}}
    {Canadian Institute for Theoretical Astrophysics}
    {Wrote a computer program to search for objects in the outer solar system using Hubble Space Telescope data---the resulting paper was published in the Astrophysical Journal.}
\end{entrylist}

\section{current volunteer work}
\begin{entrylist}
  \entry
    {2014-Present}
    {\emph{Youth Inpatient Volunteer}}
    {The Royal Ottawa Mental Health Centre}
    {Provide support for youth patients who are battling mental illness.}
    \end{entrylist}

\end{document}
